% !TEX root = ./Mohamed_Mostafa_Software_Engineer.tex
\documentclass[letterpaper, 11pt]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[top=0.3in, bottom=0.4in, left=0.3in, right=0.3in]{geometry}

\usepackage{import}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{fontawesome5}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{lmodern}
% Tighter spacing for compact layout
\titlespacing{\section}{0pt}{4pt}{2pt}
\setlist[itemize]{leftmargin=1.2em, topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=0pt}
\setlength{\parskip}{0pt}
\setlength{\belowdisplayskip}{0pt}
\setlength{\abovedisplayskip}{0pt}


% Font
% \renewcommand{\familydefault}{\sfdefault}

% Section formatting
\titleformat{\section}{\normalsize\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{5pt}

% Remove page numbering
\pagestyle{empty}

\begin{document}

\begin{center}
    {\LARGE \textbf{Mohamed Mostafa Nazih}}\\[0.15em]
    \textbf{Software Engineer} \\[0.15em]
    \faPhone~(+20) 111 296 1724 \quad
    \faMapMarker~Cairo, Egypt \quad
    \faEnvelope~\href{mailto:MohammedMostafaNazih@gmail.com}{MohammedMostafaNazih@gmail.com} \\[0.15em]
    {\small
    \faLinkedin~\href{http://linkedin.com/in/mohammedtv}{linkedin.com/in/mohammedtv} \quad
    \faGithub~\href{https://github.com/mo7ammedd}{github.com/mo7ammedd} \quad
    \faGlobe~\href{https://modev.me/}{modev.me}
    }
\end{center}



\section{EDUCATION}
\vspace{0.5em}
\textbf{B.Sc in Computer Science}, Suez Canal University \hfill \textbf{Oct 2021 -- Jul 2025} \\
\vspace{-1em}
\begin{itemize}[leftmargin=1.5em, nosep, itemsep=0.1em]
  \item Graduation Project Grade: Excellent
  \item Mentored newcomers and motivated them to continue learning and growing in the Backend fundamentals in Google
developer groups.
\end{itemize}


\section{EXPERIENCE}
\vspace{0.5em}
\textbf{Medica Scope} \hfill \textbf{Jul 2025 -- Present} \\
\textit{Backend Engineer \textbar{} Full-time Hybrid}
\begin{itemize}[leftmargin=1.5em, nosep, itemsep=0.1em]
  \item Developed and maintained backend services for \href{https://medicaacademy.com/}{\textbf{Medica Academy}}, an online medical education platform.
  \item Integrated the Paymob payment gateway and VdoCipher for secure video streaming and content protection.
  \item Optimized database queries and API endpoints, reducing average response time by 15\%.
\end{itemize}



\textbf{Onvo} \hfill \textbf{May 2024 -- Jul 2025} \\
\textit{Software Engineer \textbar{} Full-time, Remote}
\begin{itemize}[leftmargin=1.5em, nosep, itemsep=0.1em]
  \item Reworked the backend from PHP to Express.js, reducing load times by 20\% and improving system stability.
  \item Led the launch of Airwave, a platform for streaming podcasts and music, which attracted more than 10,000 users in the first week.
  \item Secured the backend to prevent DoS and XSS attacks, ensuring a more resilient and secure application.
\end{itemize}






\section{PROJECTS}
\vspace{0.5em}

\textbf{Aura Decor (Graduation Project) \textbar{}} ASP.NET, Redis, RabbitMQ, SQL Server
\hfill \faGithub~\textbf{\href{https://github.com/Mo7ammedd/Aura-Decor}{GitHub}} \\
\vspace{-0.6em}
\begin{itemize}[leftmargin=1.5em, nosep, itemsep=0.15em]
    \item AuraDecor is a modern furniture management system built with ASP.NET Core 8.0 using a clean architecture.
    \item It offers AI-powered text and image search, secure JWT authentication, and integrated Stripe processing.
    \item The system includes an advanced admin panel, RabbitMQ-based notifications, and Docker-ready deployment.
\end{itemize}

\vspace{0.6em}
\textbf{LSMSharp \textbar{}} C\#
\hfill \faGithub~\textbf{\href{https://github.com/Mo7ammedd/LSMSharp}{GitHub}} \\
\vspace{-0.6em}
\begin{itemize}[leftmargin=1.5em, nosep, itemsep=0.15em]
    \item Developed a high-performance LSM-Tree storage engine in C\# with ACID guarantees, leveled compaction, and crash-safe WAL.
    \item Optimized for write-heavy workloads with Bloom filters, skip lists, and low-latency read paths.
\end{itemize}

\vspace{0.6em}
\textbf{HungerStation Microservices \textbar{}} .NET 8, SQL Server, Docker, Azure Service Bus, Stripe
\hfill \faGithub~\textbf{\href{https://github.com/Mo7ammedd/HungerStation_Microservices}{GitHub}} \\
\vspace{-0.6em}
\begin{itemize}[leftmargin=1.5em, nosep, itemsep=0.15em]
    \item Designed a modular food delivery platform using Clean Architecture, DDD, CQRS, and database-per-service principles.
    \item Implemented event-driven communication with Azure Service Bus, JWT authentication, Stripe payments, and Dockerized deployment.
\end{itemize}

\vspace{0.6em}
\textbf{Talabat \textbar{}} C\#, SQL Server, Redis, Docker, Stripe
\hfill \faGithub~\textbf{\href{https://github.com/Mo7ammedd/Talabat-APIs}{GitHub}} \\
\vspace{-0.6em}
\begin{itemize}[leftmargin=1.5em, nosep, itemsep=0.15em]
    \item Built a scalable e-commerce API in .NET 6 using Clean Architecture and Stripe payment integration.
    \item Applied Repository, Specification, and Unit of Work patterns with Dockerized deployment and Redis caching.
\end{itemize}


\vspace{0.6em}
\textbf{SimuKernel \textbar{}} C\#, .NET 8
\hfill \faGithub~\textbf{\href{https://github.com/Mo7ammedd/SimuKernel}{GitHub}} \\
\vspace{-0.6em}
\begin{itemize}[leftmargin=1.5em, nosep, itemsep=0.15em]
    \item Developed an operating system simulator implementing CPU scheduling, virtual memory paging, and a mini kernel with process management.
    \item Supports Round Robin, Priority, and MLFQ schedulers with real-time visualization and detailed performance metrics.
    \item Built paging simulator with FIFO, LRU, and Optimal algorithms, providing step-by-step visualization and fault/hit statistics.
    \item Includes a mini in-memory kernel featuring boot sequence, CLI commands, process creation/termination, and memory allocation.
\end{itemize}


\section{SKILLS}
\vspace{0.5em}
\begin{itemize}[leftmargin=1.5em, nosep, itemsep=0.2em]
\item \textbf{Languages and Frameworks:} \small{C\#, ASP.NET Core, JavaScript (Node.js, Express.js, Hono, Bun), Python, C++}

\item \textbf{Databases:} \small{SQL Server, PostgreSQL, MongoDB, MySQL, MariaDB, SQLite, Redis, Memcached, AstroDB}

\item \textbf{Cloud \& DevOps:} \small{Docker, Nginx, OpenResty, Azure, AWS (EC2, S3), CI/CD (GitHub Actions, Azure DevOps)}

  \item \textbf{API \& Messaging:} \small{REST, gRPC, RabbitMQ, Azure Service Bus, Stripe, Paymob}
  \item \textbf{Testing \& Tools:} \small{xUnit, NUnit, Postman, Swagger/OpenAPI}
  \item \textbf{Miscellaneous:} \small{Algorithms, Data Structures, OOP, SOLID, Design Patterns, Git, Networking, DBMS, Operating Systems}
\end{itemize}


\section{ARTICLES}
\vspace{0.5em}

\begin{itemize}[leftmargin=1.2em, nosep, itemsep=0.3em]
  \item \textbf{Difference Between Cluster and Non-Cluster Index} — \href{https://modev.me/blog/difference-between-cluster-and-non-cluster-index}{modev.me/cluster-vs-noncluster}
  \item \textbf{3 Ways to Build Custom Middleware in ASP.NET Core} — \href{https://modev.me/blog/3-ways-to-build-custom-middleware-in-aspnet-core}{modev.me/aspnet-middleware}
  \item \textbf{Boxing and Unboxing in C\#} — \href{https://modev.me/blog/boxing-and-unboxing-in-csharp}{modev.me/boxing}
  \item \textbf{SimuKernel: OS Concepts Explained} — \href{https://modev.me/blog/simukernel-operating-system-concepts}{modev.me/simukernel}
\end{itemize}

\end{itemize}



\end{document}
